Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-04-14 paper/abstraction/paper.tex
acks
space cuts

\sysname is implemented in around 9500 lines of F\# code. The compiler accepts both concrete and abstract topologies and will generate evolution-friendly configurations for Cisco and Quagga~\cite{quagga} routers by default. The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to both test validity and minimize variables subject to the topology constraints. Since the analysis typically calls the SMT solver many times with relatively small optimization problems, we use a timeout of 200ms.

@@

We evaluate \sysname by applying it on policies for backbone and data center networks. We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.

@@

Our work is related to three threads of prior work.

\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level. These can be classified into two classes. The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}. The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations~\cite{synet-synthesis,narain+:configassure,propane}.
%, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
%Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.

@@

While not the focus of this paper, \sysname can enable operators to pick the right design for their networks, more quickly and with stronger guarantees. Today, when picking a design, operators analyze its multiple concrete instantiations because available analysis tools work with concrete topologies~\cite{condor}. This process is time-consuming and not fool-proof; analyzing large, concrete topologies (with potentially thousands of nodes) takes a lot of time and the analysis does not cover the entire space of topologies that may arise.

@@

\para{Acknowledgments}
We thank the many network engineers, especially George Chen and Lihua Yuan, who helped us understand the importance of working with abstract topologies and synthesizing templates. 
We also thank the PLDI reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.

>>>>

%\sysname is implemented in around 9500 lines of F\# code. 
The \sysname compiler generates configurations for Cisco and Quagga~\cite{quagga} routers. The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to both test validity and minimize variables subject to the topology constraints. Since the analysis typically calls the SMT solver many times with relatively small optimization problems, we use a timeout of 200ms.

@@

We evaluate \sysname by applying it on policies for backbone and data center networks. 
%We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.

@@

%Our work is related to three threads of prior work.

\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level of abstraction. These can be classified into two classes. The first class targets networks based on SDN (software-defined networking) and generates dataplane rules~\cite{foster:merlin,fattire,netgen}. The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations~\cite{synet-synthesis,narain+:configassure,propane}.
%, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
%Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.

@@

%While not the focus of this paper, \sysname can enable operators to pick the right design for their networks, more quickly and with stronger guarantees. Today, when picking a design, operators analyze its multiple concrete instantiations because available analysis tools work with concrete topologies~\cite{condor}. This process is time-consuming and not fool-proof; analyzing large, concrete topologies (with potentially thousands of nodes) takes a lot of time and the analysis does not cover the entire space of topologies that may arise.

@@

\para{Acknowledgments}
We thank the many network engineers, especially George Chen and Lihua Yuan, who helped us understand the importance of working with abstract topologies and synthesizing templates. 
We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
